Algorithmic Approaches to Match Degraded Land Impressions

### 2017-09-06 degraded-paper.Rmd
Add in feature expression for non-matches

Figure \@ref(fig:featexp) gives  feature expression for known matches, as a function of the proportion of land impression recovered. It is immediately obvious that the variability in feature expression is large when only a small fraction of the land is recovered, such as 25%. For instance, `sum_peaks` and  `cms` both drop, while `D` rises. Interestingly, some of the features are better expressed for the middle-fixed case. Overall, feature expression remains relatively consistent as long as we recover 50% or more of the land impression.

@@

>>>>

Figure \@ref(fig:featexp) gives feature expression for known matches, as a function of the proportion of land impression recovered. It is immediately obvious that the variability in feature expression is large when only a small fraction of the land is recovered, such as 25%. For instance, `sum_peaks` and  `cms` both drop, while `D` rises. Interestingly, some of the features are better expressed for the middle-fixed case. Overall, feature expression remains relatively consistent as long as we recover 50% or more of the land impression. Feature \@ref(fig:featexp2) shows the feature expression for known non-matches by comparison.

@@

```{r featexp2, echo=FALSE, fig.cap='Feature expression for known non-matches, as a function of land proportion. Patterns of feature expression as a function are far less visible in this case.'}
feature_exp2 <- CCFs_withlands_degrade %>%
    filter(!match) %>%
    dplyr::select(degrade_left, degrade_right, ccf, rough_cor, D, matches, mismatches, cms, non_cms, sum_peaks) %>%
    gather(key = feature, value = value, 3:ncol(.)) %>%
    group_by(degrade_left, degrade_right, feature) %>%
    summarise(value = mean(value, na.rm = TRUE)) %>%
    ungroup() %>%
    mutate(fixed = ifelse(degrade_left == 0 & degrade_right == 0, "full", ifelse(degrade_left == 0, "left", ifelse(degrade_right == 0, "right", "middle"))),
           level = degrade_left + degrade_right)

ggplot(data = feature_exp2, aes(x = level, y = value, colour = fixed)) +
    geom_point() +
    geom_line() +
    theme_bw() +
    theme(legend.position = "bottom") +
    scale_x_continuous(breaks = c(0, .25, .5, .75), labels = c("100%", "75%", "50%", "25%")) +
    xlab("Land Proportion") +
    facet_wrap(~feature, scales = "free_y")
```

### 2017-09-06 degraded-paper.tex
Add in feature expression for non-matches

Figure \ref{fig:featexp} gives feature expression for known matches, as
a function of the proportion of land impression recovered. It is
immediately obvious that the variability in feature expression is large
when only a small fraction of the land is recovered, such as 25\%. For
instance, \texttt{sum\_peaks} and \texttt{cms} both drop, while
\texttt{D} rises. Interestingly, some of the features are better
expressed for the middle-fixed case. Overall, feature expression remains
relatively consistent as long as we recover 50\% or more of the land
impression.

@@

>>>>

Figure \ref{fig:featexp} gives feature expression for known matches, as
a function of the proportion of land impression recovered. It is
immediately obvious that the variability in feature expression is large
when only a small fraction of the land is recovered, such as 25\%. For
instance, \texttt{sum\_peaks} and \texttt{cms} both drop, while
\texttt{D} rises. Interestingly, some of the features are better
expressed for the middle-fixed case. Overall, feature expression remains
relatively consistent as long as we recover 50\% or more of the land
impression. Feature \ref{fig:featexp2} shows the feature expression for
known non-matches by comparison.

@@

\begin{figure}[htbp]
\centering
\includegraphics{degraded-paper_files/figure-latex/featexp2-1.pdf}
\caption{\label{fig:featexp2}Feature expression for known non-matches, as a
function of land proportion. Patterns of feature expression as a
function are far less visible in this case.}
\end{figure}
